### 2020-08-06 paper/sex_selection_spacing-ver4.tex
Editing mortality section

The dependent variable is whether the child died within the first twelve
months of life.
The main set of explanatory variables consists of dummies for the spacing from
the prior birth.
Starting nine months after the prior birth, the birth interval dummies cover 12 
month periods until 57 months, which covers until 105 months after the prior birth.
I use dummies for sex of the index child and the sex composition 
of the prior children.
The birth spacing dummies, the sex of index child, and the sex composition dummies
are all interacted.
Since the actual number of abortions is unobserved, the interactions between
the sex composition of prior children and the sex of the index child serve
as proxies for the use of sex selection.
The other explanatory variables are the same as above, and estimations
are done separately by education level and parity.

I estimate the probability of infant mortality using a Logit model.
Figures \ref{fig:mortality_low_med} and \ref{fig:mortality_high_highest} present 
the predicted probability of the second child dying within the first year at the 
possible combinations of index child sex, sex composition of prior children, and 
the birth spacing dummied.%
\footnote{
The online Appendix shows the corresponding graphs for the third child.
}
All other variables take their average values.
The graphs do not show confidence intervals to ease their legibility.

An important caveat is that the estimations do not 
address potential selection problems.
For example, if women who have difficulties conceiving or carrying a pregnancy 
to term also have a higher mortality risk for their offspring, a spurious correlation 
between long birth spacing and mortality may arise \citep{Kozuki2013}. 
Unfortunately, methods used previously to address selection, such
as family fixed effects, do not work well when the number of births is
low as it is for better-educated women \citep{Kozuki2013,Molitoris2019}.
However, the fixed effects and linear probability results did not 
deviate substantially in prior research.

@@

Despite the prior findings of differential mortality by sex, there is little evidence 
that girls have substantially higher mortality risk.
There is some weak evidence that a boy born after a girl has a lower mortality
risk in the earliest periods.
This difference disappears, however, with the general decline in mortality risk.

If sex selective abortions lead to higher mortality risk, boys born after a girl 
(the solid lines)
should have an increased risk with longer spacing for the two highest education groups 
in the last two periods.
There are, however, no apparent consistent differences between these groups and the other 
potential combinations.

% line 3661 in an_infant_mortality.log
The raw numbers for women with the most uneven sex ratio also suggests that even with 
high use of sex selection there is no impact on child mortality. 
A total of 1,004 women with twelve or more years of
education and no boys at the start of the third spell in the last
period, had a third child, of which 685 were boys. 
Of these 685 boys, only six died within the first year of life.
Half of those who died were born in the 9-32 months interval, and none in 57 months 
or longer interval.

>>>>

The dependent variable is whether the child died within the first twelve months of life.
The main set of explanatory variables consists of dummies for the spacing from
the prior birth.
The birth interval dummies cover 12 month periods, starting nine months after the prior 
birth, until the 57 months dummy, which covers until 105 months after the prior birth.
I use dummies for sex of the index child and the sex composition 
of the prior children.
The birth spacing dummies, the sex of index child, and the sex composition dummies
are all interacted.
Since the actual number of abortions is unobserved, the interactions between
the sex composition of prior children and the sex of the index child serve
as proxies for the use of sex selection.
The other explanatory variables are the same as above, and estimations
are done separately by education level and parity.

I estimate the probability of infant mortality using a Logit model.
Figures \ref{fig:mortality_low_med} and \ref{fig:mortality_high_highest} show 
the predicted probability of the second child dying within the first year at the 
possible combinations of index child sex, sex composition of prior children, and 
birth spacing, with all other variables at their average values.%
\footnote{
The online Appendix shows the corresponding graphs for the third child.
}
The graphs do not show confidence intervals to improve legibility.

An important caveat is that the estimations do not 
address potential selection problems.
For example, suppose women who have diﬀiculties conceiving or carrying a pregnancy to 
term also have a higher mortality risk for their offspring. 
In that case, a spurious correlation between long birth spacing and mortality may arise 
\citep{Kozuki2013}. 
Unfortunately, methods to address selection, such as family fixed effects, do not work 
well when the number of births is as low as for better-educated women 
\citep{Kozuki2013,Molitoris2019}.
However, the fixed effects and linear probability results did not 
deviate substantially in prior research.

@@

Despite the prior findings of differential mortality by sex, there is little evidence 
that girls have substantially higher mortality risk.
There is some weak evidence that a boy born after a girl has a lower mortality
risk in the earliest periods.
However, this difference disappears with the general decline in mortality risk.

Despite the concern that multiple abortions might increase mortality risk by shortening 
the interval between pregnancies, there is no evidence for this effect. 
Suppose sex-selective abortions lead to higher mortality risk. In that case, boys born 
after a girl---the solid lines---should have an increased risk with longer spacing for 
the two highest education groups in the last two periods.
However, there are no apparent consistent differences between these groups and the other 
potential combinations. 
The same holds for the third spell.

% line 3661 in an_infant_mortality.log
The raw numbers for women with the most uneven sex ratio also suggest that even with 
very high use of sex selection, there is no impact on child mortality. 
A total of 1,004 women with twelve or more years of education and no boys at the start of 
the third spell in the last period, had a third child, of which 685 were boys. 
Of these 685 boys, only six died within the first year of life. 
Half of those who died were born in the 9-32 months interval, and none in the 57 months 
and up interval.
